Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-30 dit-paper_ieee.tex
typos, style

	We observe that the more we are close to the implicit deadline case ($CDF = 0$), the less systems have FPDIT. This is easily explained by the fact that a lower CDF means more idle instant for each task, and thus more opportunities for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to happen, a higher number of tasks results in a decrease in FPDIT density.

@@

		\subsubsection{Job arrival and deadline}
			Consider an interval $[t_1, t_2]$. If $t_2$ is an instant without any job
			deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to
			$\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.

			A similar argument can be made if $t_1$ is an instant without any job arrival
			(and $t_1^*$ is the earliest arrival after $t_1$). We can thus restricts
			ourselves to intervals where $t_1$ is an instant with at least one job
			arrival, and $t_2$ is an instant with at least one job deadline.

@@

			\begin{figure}[h]
				\[
					\begin{array}{r||c|c|c|l}
									& \text{Incomplete} & \text{Transitive} & \text{Stationary} & \cdots \\
						\text{Name} & \text{period} 	& \text{period} 	& \text{period}  	& \\ \hline
						\text{size} & O_{max} 			& H 				& H 				& \cdots \\ \hline
						t \geqslant & 0 				& O_{max} 			& O_{max} + H 		& \cdots
					\end{array}
				\]
				\begin{center}
				\caption{Behavior of an asynchronous system under EDF.}
				\label{fig:asyncBehavior}
				\end{center}
			\end{figure}

As shown in Fig. \ref{fig:asyncBehavior}, the system begins in the \emph{incomplete period}, where all tasks are not in the system. Then, after $O_{max}$ time units, every tasks is in the system and the \emph{transitive period} begins. Then, after $O_{max} + H$ time units, the system is faced with the same pattern of arrival as in $O_{max}$. However, because in $O_{max} + H$ every task is in the system and in $O_{max}$ some were missing, the state of the system will be different. The \emph{stationary period} then begins. It is only after $O_{max} + 2H$ time units that the system comes back into a state in which we can be sure it has been before.

>>>>

	We observe that the closer we are to the implicit deadline case ($CDF =
	0$), the fewer systems have a FPDIT. This is easily explained by the fact that
	a lower CDF means more idle instants for each task, and thus more opportunities
	for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to
	happen, a higher number of tasks results in a decrease in FPDIT density.

@@

		\subsubsection{Job arrival and deadline}
			Consider a time interval $[t_1, t_2]$. If $t_2$ is an instant without any
			job deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to
			$\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.

			A similar argument can be made if $t_1$ is an instant without any job arrival
			(and $t_1^*$ is the earliest arrival after $t_1$). We can thus restrict
			ourselves to intervals where $t_1$ is an instant with at least one job
			arrival, and $t_2$ is an instant with at least one job deadline.

@@

			\begin{figure}[h]
				\[
					\begin{array}{r||c|c|c|l}
									& \text{Incomplete} & \text{Transient}	& \text{Stationary} & \cdots \\
						\text{Name} & \text{period} 	& \text{period} 	& \text{period}  	& \\ \hline
						\text{size} & O_{max} 			& H 				& H 				& \cdots \\ \hline
						t \geqslant & 0 				& O_{max} 			& O_{max} + H 		& \cdots
					\end{array}
				\]
				\begin{center}
				\caption{Behavior of an asynchronous system under EDF.}
				\label{fig:asyncBehavior}
				\end{center}
			\end{figure}

			As shown in Fig. \ref{fig:asyncBehavior}, the system begins in the
			\emph{incomplete period}, where all tasks are not in the system. Then, after
			$O_{max}$ time units, every tasks is in the system and the \emph{transient
			period} begins. Then, after $O_{max} + H$ time units, the system is faced
			with the same pattern of arrival as in $O_{max}$. However, because in
			$O_{max} + H$ every task is in the system and in $O_{max}$ some were missing,
			the state of the system will be different. The \emph{stationary period} then
			begins. At instant $O_{max} + 2H$ it is guaranteed that the system is in the
			exact same situation it was at instant $O_{max} + H$ (however it may be
			possible to find earlier intervals with the same property).
